Calculate all possible vegetation indices that the `hsdar` package offers.

### 2018-04-04 02_scripts/01_hyperspectral_indices/01_hs-rename-and-subset.Rmd
shiny app 2 by 2

---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Information about this script

This script accounts for either local (laptop) or server (MCCOY) runs. Path is adjusted using object `prefix`

Since this is an `.Rmd` file it cannot simply be called using `source()` or `Rscript` (server).

Instead, please use the [custom function `runAllChunks()`](http://stackoverflow.com/a/24754637/4185785) inside an R console with the `.Rmd` file as input. 
It is recommended to put this function into your .Rprofile to have it available whenever you start an R session.

@@

```{r}
library(sf)
library(raster)
library(magrittr)
library(here)
library(purrr)
library(dplyr)
```

@@

```{r}
map(list.files("/data/patrick/raw/hyperspectral/ATM", 
                    full.names = TRUE, pattern = ".tif$"),
    ~ brick(.x)) -> data_atm

all.plots <- st_read("/home/shares/data/LIFE/mod/plots/location/all.plots.shp") %>% mutate(Name = as.character(Name))
```

@@

```{r}
st_read("/data/patrick/mod/plots/location/all.plots.shp") %>% 
  mutate(Name = as.character(Name)) -> plot_locations
```

@@

## Busturi- axpe (Code B101)
```{r}
busturi1 <- raster::brick(files[[1]])

all.plots %>% 
  filter(Name == "a busturi-axpe") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

busturi1 <- raster::crop(busturi1, plot.shp)
busturi1 <- raster::mask(busturi1, plot.shp)
busturi1 <- raster::projectRaster(busturi1, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(busturi1, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/busturi.tif",
                    overwrite = TRUE)
```

## Laukiz 1, Laukiz 2, Laukiz 3 (Code B103)

```{r}
## Laukiz I
laukiz1 <- raster::brick(files[[2]])

all.plots %>% 
  filter(Name == "Laukiz I") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

laukiz1 <- raster::crop(laukiz1, plot.shp)
laukiz1 <- raster::mask(laukiz1, plot.shp)
laukiz1 <- raster::projectRaster(laukiz1, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(laukiz1, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/laukiz1.tif",
                    progress = "text", overwrite = TRUE)

## Laukiz II
laukiz2 <- raster::brick(files[[2]])

all.plots %>% 
  filter(Name == "Laukiz II") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

laukiz2 <- raster::crop(laukiz2, plot.shp)
laukiz2 <- raster::mask(laukiz2, plot.shp)
laukiz2 <- raster::projectRaster(laukiz2, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(laukiz2, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/laukiz2.tif",
                    progress = "text", overwrite = TRUE)

## Laukiz III
laukiz3 <- raster::brick(files[[2]])

all.plots %>% 
  filter(Name == "Laukiz III") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

laukiz3 <- raster::crop(laukiz3, plot.shp)
laukiz3 <- raster::mask(laukiz3, plot.shp)
laukiz3 <- raster::projectRaster(laukiz3, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(laukiz3, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/laukiz3.tif",
                    progress = "text", overwrite = TRUE)

```

## Altube (Code B111 and B211)

```{r}
altube <- raster::brick(files[[3]])

all.plots %>% 
  filter(Name == "a altube") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

altube <- raster::crop(altube, plot.shp)
altube <- raster::mask(altube, plot.shp)
altube <- raster::projectRaster(altube, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(altube, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/altube.tif", 
                    progress = "text", overwrite = TRUE) 
```

## Barazar (Code B113)

```{r}
barazar <- raster::brick(files[[4]])

all.plots %>% 
  filter(Name == "a barazar") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

barazar <- raster::crop(barazar, plot.shp)
barazar <- raster::mask(barazar, plot.shp)
barazar <- raster::projectRaster(barazar, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(barazar, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/barazar.tif",
                    progress = "text", overwrite = TRUE)
```

## Laricio defol. Urkiola (Code B114)

```{r}
Laricio.defol.urkiola <- raster::brick(files[[5]])

all.plots %>% 
  filter(Name == "Laricio defol. Urkiola.") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

Laricio.defol.urkiola <- raster::crop(Laricio.defol.urkiola, plot.shp)
Laricio.defol.urkiola <- raster::mask(Laricio.defol.urkiola, plot.shp)
Laricio.defol.urkiola <- raster::projectRaster(Laricio.defol.urkiola, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(Laricio.defol.urkiola, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/laricio-defol-urkiola.tif",
                    progress = "text", overwrite = TRUE)
```

## Aguinaga pinaster radiata (Code B123)

```{r}
aguinaga.pinaster.radiata <- raster::brick(files[[6]])

all.plots %>% 
  filter(Name == "aguinaga pinaster radiata") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

aguinaga.pinaster.radiata <- raster::crop(aguinaga.pinaster.radiata, plot.shp)
aguinaga.pinaster.radiata <- raster::mask(aguinaga.pinaster.radiata, plot.shp)
aguinaga.pinaster.radiata <- raster::projectRaster(aguinaga.pinaster.radiata, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(aguinaga.pinaster.radiata, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/aguinaga-pinaster-radiata.tif",
                    progress = "text", overwrite = TRUE)
```

## Oiartzun (Code B124)

```{r}
oiartzun <- raster::brick(files[[7]])

all.plots %>% 
  filter(Name == "Oiartzun") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

oiartzun <- raster::crop(oiartzun, plot.shp)
oiartzun <- raster::mask(oiartzun, plot.shp)
oiartzun <- raster::projectRaster(oiartzun, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(oiartzun, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/oiartzun.tif",
                    progress = "text", overwrite = TRUE)
```

## Pinast. Arza (Code B204)

```{r}
pinast.arza <- raster::brick(files[[8]])

all.plots %>% 
  filter(Name == "Pinast. Arza") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

pinast.arza <- raster::crop(pinast.arza, plot.shp)
pinast.arza <- raster::mask(pinast.arza, plot.shp)
pinast.arza <- raster::projectRaster(pinast.arza, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(pinast.arza, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/pinast-arza.tif",
                    progress = "text", overwrite = TRUE) 
```

## Pinas. Santa Koloma (Code B205)

```{r}
pinas.santa.koloma <- raster::brick(files[[9]])

all.plots %>% 
  filter(Name == "Pinas. Santa Koloma") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

pinas.santa.koloma <- raster::crop(pinas.santa.koloma, plot.shp)
pinas.santa.koloma <- raster::mask(pinas.santa.koloma, plot.shp)
pinas.santa.koloma <- raster::projectRaster(pinas.santa.koloma, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(pinas.santa.koloma, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/pinas-santa-koloma.tif",
                    progress = "text", overwrite = TRUE)
```

## Rad. Menagaray 1 and Rad. Mengaray 2 (Code B206)

```{r}
## Rad. Menagaray 1
rad.menagaray.1 <- raster::brick(files[[10]])

all.plots %>% 
  filter(Name == "Rad. Menagaray 1") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

rad.menagaray.1 <- raster::crop(rad.menagaray.1, plot.shp)
rad.menagaray.1 <- raster::mask(rad.menagaray.1, plot.shp)
rad.menagaray.1 <- raster::projectRaster(rad.menagaray.1, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(rad.menagaray.1, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/rad-menagaray-1.tif",
                    progress = "text", overwrite = TRUE)

## Rad. Menagaray 2
rad.menagaray.2 <- raster::brick(files[[10]])

all.plots %>% 
  filter(Name == "Rad. Menagaray 2") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

rad.menagaray.2 <- raster::crop(rad.menagaray.2, plot.shp)
rad.menagaray.2 <- raster::mask(rad.menagaray.2, plot.shp)
rad.menagaray.2 <- raster::projectRaster(rad.menagaray.2, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(rad.menagaray.2, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/rad-menagaray-2.tif",
                    progress = "text", overwrite = TRUE) 
```

## Ayala_aiara / Luiando (Code B207)

```{r}
ayala.aiara <- raster::brick(files[[11]])

all.plots %>% 
  filter(Name == "Ayala/Aiara") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

ayala.aiara <- raster::crop(ayala.aiara, plot.shp)
ayala.aiara <- raster::mask(ayala.aiara, plot.shp)
ayala.aiara <- raster::projectRaster(ayala.aiara, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(ayala.aiara, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/ayala-aiara.tif",
                    progress = "text", overwrite = TRUE)
```

## Silvest. Nograro (Code B208)

```{r}
silvest.nograro <- raster::brick(files[[12]])

all.plots %>% 
  filter(Name == "Silvest. Nograro") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

silvest.nograro <- raster::crop(silvest.nograro, plot.shp)
silvest.nograro <- raster::mask(silvest.nograro, plot.shp)
silvest.nograro <- raster::projectRaster(silvest.nograro, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(silvest.nograro, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/silvest-nograro.tif",
                    progress = "text", overwrite = TRUE)
```

## Caranca (Code B209)

```{r}
caranca <- raster::brick(files[[13]])

all.plots %>% 
  filter(Name == "a caranca") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

caranca <- raster::crop(caranca, plot.shp)
caranca <- raster::mask(caranca, plot.shp)
caranca <- raster::projectRaster(caranca, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(caranca, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/caranca.tif",
                    progress = "text", overwrite = TRUE)
```

## Picea Abornicano (Code B210)

```{r}
picea.abornicano <- raster::brick(files[[14]])

all.plots %>% 
  filter(Name == "Picea Abornicano") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

picea.abornicano <- raster::crop(picea.abornicano, plot.shp)
picea.abornicano <- raster::mask(picea.abornicano, plot.shp)
picea.abornicano <- raster::projectRaster(picea.abornicano, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(picea.abornicano, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/picea-abornicano.tif",
                    progress = "text", overwrite = TRUE)
```

## Douglas 1 and Douglas 2 and Rad. Altube (Code B212)

Code 211 bzw. file[[15]] == Altube

```{r}
## douglas 1
douglas.1 <- raster::brick(files[[16]])

all.plots %>% 
  filter(Name == "douglas 1") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

douglas.1 <- raster::crop(douglas.1, plot.shp)
douglas.1 <- raster::mask(douglas.1, plot.shp)
douglas.1 <- raster::projectRaster(douglas.1, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(douglas.1, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/douglas.1.tif",
                    progress = "text", overwrite = TRUE)

## douglas 2
douglas.2 <- raster::brick(files[[16]])

all.plots %>% 
  filter(Name == "douglas 2") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

douglas.2 <- raster::crop(douglas.2, plot.shp)
douglas.2 <- raster::mask(douglas.2, plot.shp)
douglas.2 <- raster::projectRaster(douglas.2, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(douglas.2, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/douglas-2.tif",
                    progress = "text", overwrite = TRUE)

## rad. altube
rad.altube <- raster::brick(files[[16]])

all.plots %>% 
  filter(Name == "Rad. Altube") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

rad.altube <- raster::crop(rad.altube, plot.shp)
rad.altube <- raster::mask(rad.altube, plot.shp)
rad.altube <- raster::projectRaster(rad.altube, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(rad.altube, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/rad-altube.tif",
                    progress = "text", overwrite = TRUE)
```

## Otxandio and Laricio defol. Olaeta (Code B215)

```{r}
## otxandio
otxandio <- raster::brick(files[[17]])

all.plots %>% 
  filter(Name == "a otxandio") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

otxandio <- raster::crop(otxandio, plot.shp)
otxandio <- raster::mask(otxandio, plot.shp)
otxandio <- raster::projectRaster(otxandio, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(otxandio, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/otxandio.tif",
                    progress = "text", overwrite = TRUE)

## Laricio defol. Olaeta
laricio.defol.olaeta <- raster::brick(files[[17]])

all.plots %>% 
  filter(Name == "Laricio defol. Olaeta. pol") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

laricio.defol.olaeta <- raster::crop(laricio.defol.olaeta, plot.shp)
laricio.defol.olaeta <- raster::mask(laricio.defol.olaeta, plot.shp)
laricio.defol.olaeta <- raster::projectRaster(laricio.defol.olaeta, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(laricio.defol.olaeta, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/laricio-defol-olaeta.tif",
                    progress = "text", overwrite = TRUE)
```

## Douglas Legutio (Code B317 and B318)
Here B317 is taken
```{r}
douglas.legutio <- raster::brick(files[[18]])

all.plots %>% 
  filter(Name == "Douglas Legutio") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

douglas.legutio <- raster::crop(douglas.legutio, plot.shp)
douglas.legutio <- raster::mask(douglas.legutio, plot.shp)
douglas.legutio <- raster::projectRaster(douglas.legutio, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(douglas.legutio, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/douglas-legutio.tif",
                    progress = "text", overwrite = TRUE)
```
## Laricio Gatzaga (Code B319)

```{r}
laricio.gatzaga <- raster::brick(files[[20]])

all.plots %>% 
  filter(Name == "Laricio defol.Gatzaga") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

laricio.gatzaga <- raster::crop(laricio.gatzaga, plot.shp)
laricio.gatzaga <- raster::mask(laricio.gatzaga, plot.shp)
laricio.gatzaga <- raster::projectRaster(laricio.gatzaga, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(laricio.gatzaga, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/laricio.gatzaga.tif",
                    progress = "text", overwrite = TRUE)
```
## Azaceta (Code B320)

```{r}
azaceta <- raster::brick(files[[21]])

all.plots %>% 
  filter(Name == "a azaceta") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

azaceta <- raster::crop(azaceta, plot.shp)
azaceta <- raster::mask(azaceta, plot.shp)
azaceta <- raster::projectRaster(azaceta, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(azaceta, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/azaceta.tif",
                    progress = "text", overwrite = TRUE)
```
## Gipuzkoa and Sequoia Legorreta (Code B321)

```{r}
## gipuzkoa
gipuzkoa <- raster::brick(files[[22]])

all.plots %>% 
  filter(Name == "a gipuzkoa") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

gipuzkoa <- raster::crop(gipuzkoa, plot.shp)
gipuzkoa <- raster::mask(gipuzkoa, plot.shp)
gipuzkoa <- raster::projectRaster(gipuzkoa, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(gipuzkoa, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/gipuzkoa.tif",
                    progress = "text", overwrite = TRUE)

## Sequoia Legorreta
sequoia.legorreta <- raster::brick(files[[22]])

all.plots %>% 
  filter(Name == "Sequoia Legorreta") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

sequoia.legorreta <- raster::crop(sequoia.legorreta, plot.shp)
sequoia.legorreta <- raster::mask(sequoia.legorreta, plot.shp)
sequoia.legorreta <- raster::projectRaster(sequoia.legorreta, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(sequoia.legorreta, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/sequoia.legorreta.tif",
                    progress = "text", overwrite = TRUE)
```
## Douglas Albiztur (Code B322)

```{r}
douglas.albiztur <- raster::brick(files[[23]])

all.plots %>% 
  filter(Name == "Douglas Albiztur") %>% 
  st_transform("+proj=utm +zone=30 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") %>% 
  as("Spatial") -> plot.shp

douglas.albiztur <- raster::crop(douglas.albiztur, plot.shp)
douglas.albiztur <- raster::mask(douglas.albiztur, plot.shp)
douglas.albiztur <- raster::projectRaster(douglas.albiztur, crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

raster::writeRaster(douglas.albiztur, "/home/shares/data/LIFE/mod/hyperspectral/atm-cropped/douglas-albiztur.tif",
                    progress = "text", overwrite = TRUE)
```

>>>>

---
title: "R Notebook"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE)
```

@@

```{r, results='hide'}
library(sf)
library(raster)
library(magrittr)
library(purrr)
library(dplyr)
```

@@

```{r}
map(list.data_atm("/data/patrick/raw/hyperspectral/ATM", 
                    full.names = TRUE, pattern = ".tif$"),
    ~ brick(.x)) -> data_atm
```

@@

```{r}
st_read("/data/patrick/mod/plots/location/plot_locations.shp") %>% 
  mutate(Name = as.character(Name)) -> plot_locations
```

@@

```{r}
process_hyperspec <- function(name_id, name_out, index) {

  image <- data_atm[[index]]

  plot_locations %>% 
    filter(Name == name_id) %>% 
    st_transform(25830) %>% 
    as("Spatial") -> shape_single_plot

  image %>% 
    crop(shape_single_plot) %>% 
    mask(shape_single_plot) %>% 
    projectRaster(crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs") %>% 
    writeRaster(glue("/data/patrick/mod/hyperspectral/atm-cropped/{name_out}.tif"),
                overwrite = TRUE)
  cat(glue("Finished {name_out}."))
}
```

# Create dictionaries to apply over

```{r}
name_id = c("a busturi-axpe", "Laukiz I", "Laukiz II", "Laukiz III", "a altube", 
            "a barazar", "Laricio defol. Urkiola.", "aguinaga pinaster radiata",
            "Oiartzun", "Pinast. Arza", "Pinas. Santa Koloma", "Rad. Menagaray 1",
            "Rad. Menagaray 2", "Ayala/Aiara", "Silvest. Nograro", "a caranca",
            "Picea Abornicano", "douglas 1", "douglas 2", "Rad. Altube", 
            "a otxandio", "Laricio defol. Olaeta. pol", "Douglas Legutio", 
            "Laricio defol.Gatzaga", "a azaceta", "a gipuzkoa", 
            "Sequoia Legorreta", "Douglas Albiztur")
name_out = c("busturi", "laukiz1", "laukiz2", "laukiz3", "altube", "barazar", 
             "laricio-defol-urkiola", "aguinaga-pinaster-radiata", "oiartzun",
             "pinast-arza", "pinas-santa-koloma", "rad-menagaray-1",
             "rad-menagaray-2", "luiando", "silvest-nograro", "caranca",
             "picea-abornicano", "douglas-1", "douglas-2", "rad-altube",
             "otxandio", "laricio-defol-olaeta", "douglas-legutio",
             "laricio-gatzaga", "azaceta", "gipuzkoa", "sequoia-legorreta", 
             "douglas-albiztur")
index = c(1, 2, 2, 2, 3, 4, 5, 6, 7, 8, 9, 10, 10, 11, 12, 13, 14, 16, 16, 16,
          17, 17, 18, 20, 21, 22, 22, 23)
```

Now let's map over all entries in the vectors specified.

```{r}
pwalk(list(name_id, name_out, index), ~ process_hyperspec(..1, ..2, ..3))
```

```{r}
sessionInfo()
```

### 2018-04-04 02_scripts/01_hyperspectral_indices/04_hyperspectral-all-vegindex.Rmd
shiny app 2 by 2

---
title: "Calculate all possible vegetation indices that the `hsdar` package offers."
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Information about this script

This script accounts for either local (laptop) or server (MCCOY) runs. Path is adjusted using object `prefix`

Since this is an `.Rmd` file it cannot simply be called using `source()` or `Rscript` (server).

Instead, please use the [custom function `runAllChunks()`](http://stackoverflow.com/a/24754637/4185785) inside an R console with the `.Rmd` file as input. 
It is recommended to put this function into your .Rprofile to have it available whenever you start an R session.

```{r}
pacman::p_load(raster, hsdar, pbapply, parallel, rasterFunctions, tidyverse)
```

@@

```{r}
wavelength <- readRDS("/home/shares/data/LIFE/mod/hyperspectral/wavelength.Rds")
```

# List files

```{r}
files <- list.files("/home/shares/data/LIFE/mod/hyperspectral/atm-cropped", 
                    pattern = ".tif$", full.names = TRUE)
```

# read in files as "RasterBrick"
```{r}
spectral_data <- lapply(files, function(x) brick(x))
```

# make class "HyperSpecRaster"

```{r}
hyperspecs <- lapply(spectral_data, function(x) hsdar::HyperSpecRaster(x, wavelength))
```

# account for use on local laptop or server
```{r}
if (detectCores() > 10) {
  cores <- 28
} else (cores <- 1)
```

# do calculation

Runtime server: ~ 1 min
Runtime MBP: ~ 10 mins

@@

Specify vegetation indices.

```{r}
# subset for test purposes
# hyperspecs <- list(hyperspecs[[17]])

# specify which indices to calculate WITH DERIVATION INDICES
indices <- c("Boochs", "Boochs2","CARI", "Carter", "Carter2", "Carter3", "Carter4", "Carter5",
             "Carter6", "CI", "CI2", "ClAInt", "CRI1", "CRI2", "CRI3", "CRI4",
             "D1", "D2",
             "Datt", "Datt2", "Datt3", "Datt4", "Datt5", "Datt6", "DD", "DDn", "DPI", "DWSI4",
             "EGFR", "EVI", "GDVI_2", "GDVI_3", "GDVI_4", "GI", "Gitelson",
             "Gitelson2", "GMI1", "GMI2", "Green NDVI", "Maccioni", "MCARI",
             "MCARI2", "mND705", "mNDVI", "MPRI", "MSAVI", "mSR",
             "mSR2", "mSR705", "MTCI", "MTVI", "NDVI", "NDVI2", "NDVI3",
             "NPCI", "OSAVI", "PARS", "PRI", "PRI_norm", "PRI*CI2", "PSRI",
             "PSSR", "PSND","SPVI", "PWI", "RDVI", "REP_Li", "SAVI", "SIPI",
             "SPVI","SR", "SR1", "SR2", "SR3", "SR4", "SR5", "SR6", "SR7",
             "SR8", "Sum_Dr1", "Sum_Dr2", "SRPI", "TCARI", "TCARI2", "TGI", "TVI", "Vogelmann",
             "Vogelmann2", "Vogelmann3", "Vogelmann4")
# length(indices)
```

# do veg. indices calculation

```{r }
hyperspecs %>% 
  pblapply(function(x) 
    vegindex(x, indices, filename = 
             gsub(".tif", ".grd", 
                  "/home/shares/data/LIFE/mod/hyperspectral/all-veg-indices/",
                    "all-veg-indices-", basename(x@file@name)), na.rm = T,
             bnames = indices), cl = cores) -> rasters

# mapview(tmp[[1]])
```

>>>>

---
title: "Calculate all possible vegetation indices that the `hsdar` package offers."
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE)
```

# Load packages

```{r}
library(raster)
library(hsdar)
library(pbmcapply)
library(magrittr)
library(purrr)
library(glue)
```

@@

```{r}
wavelength <- readRDS("/data/patrick/mod/hyperspectral/wavelength.Rds")
```

## list files

```{r}
list.files("/data/patrick/mod/hyperspectral/atm-cropped", 
                    pattern = ".tif$", full.names = TRUE) %>% 
  map(~ brick(.x)) -> spectral_data
```

# Coerce to class "HyperSpecRaster"

```{r}
hyperspecs = map(spectral_data, function(x) HyperSpecRaster(x, wavelength))
```

# Specify indices

```{r}
# specify which indices to calculate WITH DERIVATION INDICES
indices <- c("Boochs", "Boochs2","CARI", "Carter", "Carter2", "Carter3", "Carter4", "Carter5",
             "Carter6", "CI", "CI2", "ClAInt", "CRI1", "CRI2", "CRI3", "CRI4",
             "D1", "D2",
             "Datt", "Datt2", "Datt3", "Datt4", "Datt5", "Datt6", "DD", "DDn", "DPI", "DWSI4",
             "EGFR", "EVI", "GDVI_2", "GDVI_3", "GDVI_4", "GI", "Gitelson",
             "Gitelson2", "GMI1", "GMI2", "Green NDVI", "Maccioni", "MCARI",
             "MCARI2", "mND705", "mNDVI", "MPRI", "MSAVI", "mSR",
             "mSR2", "mSR705", "MTCI", "MTVI", "NDVI", "NDVI2", "NDVI3",
             "NPCI", "OSAVI", "PARS", "PRI", "PRI_norm", "PRI*CI2", "PSRI",
             "PSSR", "PSND","SPVI", "PWI", "RDVI", "REP_Li", "SAVI", "SIPI",
             "SPVI","SR", "SR1", "SR2", "SR3", "SR4", "SR5", "SR6", "SR7",
             "SR8", "Sum_Dr1", "Sum_Dr2", "SRPI", "TCARI", "TCARI2", "TGI", "TVI", "Vogelmann",
             "Vogelmann2", "Vogelmann3", "Vogelmann4")
# length(indices)
```

# Calculate vegetation indices

@@

```{r, cache=FALSE}
tmp <- pbmclapply(hyperspecs, function(x) 
  vegindex(x, indices, 
           filename = 
             str_replace(glue("/data/patrick/mod/hyperspectral/all-veg-indices/{name}",
                              name = basename(x@file@name)), ".tif", ".grd"), 
           na.rm = TRUE, bnames = indices), mc.cores = 28)
```
